Canonical rings of rational divisors on projective space and Hirzebruch surfaces

### 2015-07-14 surfaces-write-up/surface-write-up.tex
fix generators 1pt

\noindent
where $\vec{y} \in \mss_i$ and $\vec{w} \in \mss_j$ are the unique
vectors such that $\vec{y} \prec \vec{w}$.
\end{thm}

@@

Now we show that no further generators are necessary. As done in
the proof of the $\bp^1$ case by O'Dorney \cite[Theorem 6]
{dorney:canonical}, each lattice point $(\beta, \gamma) \in
\bz_{\geq 0}^2$ such that $c \leq d \alpha$ is a non-negative
linear combination of $\vec{x}_i$ and $\vec{x}_{i + 1}$ where
$\vec{x}_i := (d_i, c_i) \in \bz^2$. Consequently, if $(\beta,
\gamma) = \ell_1 (d_i, c_i) + \ell_2 (d_{i + 1}, c_{i + 1})$ for
$\ell_1, \ell_2 \in \bz_{ \geq 0}$, then any element $\frac{u^{\beta}
x^{\vec{v}}} {x_k^{ \gamma}} \in R_D$ is expressible as
\begin{align*}
	\frac{u^{\beta} x^{\vec{v}}} {x_k^{\gamma}} = \left(\frac{u^{d_i}
	x^{\vec{w}}} {x_k^{c_i}}\right)^{\ell_1} \left(\frac{u^{d_{i + 1}}
	x^{\vec{z}}} {x_k^{c_{i + 1}}}\right)^{\ell_2}
\end{align*}

\noindent
for some $\vec{w} \in \mss_i, \vec{z} \in \mss_{i + 1}$. But these
are precisely powers of two generators of the form $F_i^{\vec{w}}$
and $F_{d_{i + 1}}^{\vec{z}}$ as prescribed in the theorem statement.

>>>>

\noindent
where $\vec{y}$ and $\vec{w}$ are the unique
vectors in $\mss_i$ and $\mss_j$, respectively, such that $\vec{y}
\prec \vec{w}$.
\end{thm}

@@

Now we show that no further generators are necessary. As done in
the proof of the $\bp^1$ case by O'Dorney \cite[Theorem 6]
{dorney:canonical}, each lattice point $(\beta, \gamma) \in
\bz_{\geq 0}^2$ such that $c \leq d \alpha$ is a non-negative
linear combination of $\vec{x}_i$ and $\vec{x}_{i + 1}$ where
$\vec{x}_i := (d_i, c_i) \in \bz^2$. Let $(\beta, \gamma) = \ell_1
(d_i, c_i) + \ell_2 (d_{i + 1}, c_{i + 1})$ for $\ell_1, \ell_2 \in
\bz_{\geq 0}$. Consequently, any element $\frac{u^{\beta}
x^{\vec{v}}} {x_k^{ \gamma}} \in R_D$ is expressible as
\begin{align*}
	\frac{u^{\beta} x^{\vec{v}}} {x_k^{\gamma}} = \left(\frac{u^{d_i}}
	{x_k^{c_i}}\right)^{\ell_1} \left(\frac{u^{d_{i + 1}}}
	{x_k^{c_{i + 1}}}\right)^{\ell_2} x^{\vec{v}}.
\end{align*}

\noindent
We can break $\vec{v}$ into a sum of $\ell_1$ many vectors
$\vec{w}_{(j)}$ in $\mss_2$ and $\ell_2$ many vectors $\vec{z}_{(k)}$
in $\mss_2$ to give a decomposition
\begin{align*}
	\frac{u^{\beta} x^{\vec{v}}} {x_k^{\gamma}}	= \prod_{j = 1}
	^{\ell_1} \frac{u^{d_i} x^{\vec{w}_{(j)}}} {x_k^{c_i}}
	\prod_{k = 1}^{\ell_2} \frac{u^{d_{i + 1}} x^{\vec{z}_{(k)}}}
	{x_k^{c_{i + 1}}}
\end{align*}
into products of generators $F_i^{\vec{w}_{(j)}}$
and $F_{d_{i + 1}}^{\vec{z}_{(k)}}$ which are in the form
prescribed in the theorem statement.
